---
title: "Cor-relation among House Price Index and GDP using time series"
output:
  pdf_document: default
  html_notebook: default
---

importing libraries 

```{r}
library("tidyverse")
library("dplyr")
library("tidyr")
library("zoo")
```

importing HDI and GDP files

```{r}
House_Price_Index <- read.csv("C:/Users/HP/Downloads/House_Price_Index.csv")
GDP_Index <- read.csv("C:/Users/HP/Downloads/GDP-table-no.csv")

```

Scrunitized HPI and GDP files and make new data sets

```{r}
hpidata <- House_Price_Index[6:53,2:15]
gdpdata <- GDP_Index[4:46,3:12] 
```

convert first row to be header

```{r}
colnames(hpidata) = hpidata[1, ] 
colnames(gdpdata) = gdpdata[1, ]
```

Removing first row

```{r}
hpidata = hpidata[-1, ]
gdpdata = gdpdata[-1, ]
```

Two datasets of HPI values and GDP values
```{r}
hpidata <- hpidata %>% 
  select("Quarter","ALL INDIA")
gdpdata <- gdpdata %>% 
  select("Quarter","GDP at market prices")
```

Indexing reset to 1

```{r}
row.names(hpidata) <- NULL
row.names(gdpdata) <- NULL
```

new data values starting from year 2011 in HPI to compare with GDP from year 2011

```{r}
hpidata <- hpidata[5:46, ]
row.names(hpidata) <- NULL
```

converting the values of the variable ALL INDIA HPI and GDP at market prices characters to numeric values

```{r}
hpidata$`ALL INDIA` <- as.numeric(hpidata$`ALL INDIA`)
class(hpidata$`ALL INDIA`)
gdpdata$`GDP at market prices` <- as.numeric(gdpdata$`GDP at market prices`)
class(gdpdata$`GDP at market prices`)
```

date format in Quarter and Year 

```{r}
hpidata$Quarter <- as.yearqtr(hpidata$Quarter, "Q%q.%Y")
class(hpidata$Quarter)
```

new data frame of HPI and GDP in one file by having three columns Quarter, HPI and GDP values in one frame

```{r}
HPI_GDP <- data.frame(hpidata$Quarter,hpidata$`ALL INDIA`,gdpdata$`GDP at market prices`)
colnames(HPI_GDP) <- c("Quarter","Housing Price Index","Gross Domastic Product")
View(HPI_GDP)
```

Growth rate of gdp
```{r}
k <- gdpdata$`GDP at market prices`
growth_rate <- function(x)(x/lag(x)-1)*100 
HPI_GDP$`GDP at market prices` <- round(growth_rate(gdpdata$`GDP at market prices`),2) 
```

Make the data frame into time series data

```{r}
library(xts)
class(HPI_GDP$Quarter)
HPI_GDP <- xts(HPI_GDP[,-1], order.by = HPI_GDP$Quarter)
HPI_GDP <- HPI_GDP[-1,]
```


Plotting GDP and House Price Index
```{r}
mydata <- merge(Housing Price Index,GDP at market prices) %>% fortify %>%
  tidyr::gather(Variable, Value, -Index)

ggplot(HPI_GDP$`Housing Price Index`) + geom_line(HPI_GDP$`GDP at market prices`,mapping = (aes(HPI_GDP$`Housing Price Index`, HPI_GDP$`GDP at market prices`))) 
```

